---
title: "hw1"
author: "Shuo Niu"
date: "2017/1/29"
output: html_document
---
```{r}
library("astro")
library("tidyverse")
```


# Data Manipulation

```{r}
# data input
d206 <- as_tibble(read.fitstab(file = "spec-0309-51994-0206.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0206")
d570 <- as_tibble(read.fitstab(file = "spec-0297-51959-0570.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0570")
d132 <- as_tibble(read.fitstab(file = "spec-0289-51990-0132.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0132")
d080 <- as_tibble(read.fitstab(file = "spec-0385-51783-0080.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0080")
d403 <- as_tibble(read.fitstab(file = "spec-0341-51690-0403.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0403")
d579 <- as_tibble(read.fitstab(file = "spec-1353-53083-0579.fits")) %>% filter(and_mask == 0) %>% mutate(wavelength = 10^loglam, variance = 1/ivar,label = "d0579")

# Unite all data
dsum <- bind_rows(d132,d206,d080,d403,d570,d579) %>% select(label,flux,wavelength,variance,model)
```

# Data Visualization

# Visualization 

- Six Panel Plot

```{r}
dsum %>% ggplot(mapping = aes(x = wavelength,y = flux, color = label)) + geom_line() + labs(title  = "Points Plot") + theme(plot.title = element_text(hjust = 0.5)) + facet_wrap( ~ label, nrow = 3,scales = "free")
```

- One Panel Points Plot
```{r}
dsum %>% ggplot(mapping = aes(x = wavelength,y = flux, color = label)) + geom_line() + labs(title  = "Points Plot") + theme(plot.title = element_text(hjust = 0.5))
```

- Smooth Plot

```{r}
dsum %>% ggplot(mapping = aes(x = wavelength,y = flux, color = label)) + geom_smooth(method = "loess") + labs(title  = "Smooth Plot") + theme(plot.title = element_text(hjust = 0.5))
```

# Method to find the nearest galaxy

My idea is to fit a polynomial regression model of the 0579 data. In the model, wavelength is the independent variable as the flux is the dependent one.

Then, use this model to predict the flux value of the other 5 datasets. Calculate the mean absolute prediction error of each other dataset. 

# Difficulties

The six datasets have different number of samples. It leads to some diffculities to plot and analysis.
Here, I use the dplyr and ggplot packages to solve the problem.

